Learning Network Size while Training with ShrinkNets

### 2018-02-09 paper/ICML/evaluation.tex
Add numbers to the evaluation

\item \srm{something else?}

@@

The results are shown in the top figure of \cref{figure_CIFAR10}, with blue dots
indicating models produced by \shrink and orange dots indicating static networks. 
For each
model, we plot its accuracy and model size. The lines show the Pareto frontier
of models in each of the two optimization settings. ShrinkNets explore the
trade-off between model size and accuracy more effectively. 
\srm{Would be good
to show Lambda values on the figure somehow.  } \srm{I thought we were going to
summarize with distributional plots instead of Pareto frontiers?} 
%\srm{Summarize
%more quantitatively -- best model performance, model performance drop off for a
%factor of 10 reduction in seize, etc. so that we can repeat a quantitative claim
%in the intro, i.e., ``Note that the best performing ShrinkNets models has 9x.x\%
%accuracy while the best static model has 9x.x\% accuracy, while the ShrinkNets
%model is x times smaller.  In addition, if we give up just 1\% error, ShrinkNets
%finds a model that is z times smaller.'' (If we do this, would be good to
%highlight these points in the figure somehow)}

Note that the best performing ShrinkNets models has \ra{xx} accuracy while the
best static model has \ra{xx} accuracy, while the ShrinkNets model is \ra{xx}
times smaller. In addition, if we give up just 1\% error, ShrinkNets finds a
model that is \ra{xx} times smaller.

@@

Note that the best performing ShrinkNets models has \ra{xx} accuracy while the
best static model has \ra{xx} accuracy, while the ShrinkNets model is \ra{xx}
times smaller. In addition, if we give up just 1\% error, ShrinkNets finds a
model that is \ra{xx} times smaller.

@@

A key takeaway of these speedup results is that, unlike local sparsity compression methods, our methods' improvement on size translates directly to higher throughput at inference time. \srm{Can we cite something showing that local sparsity does not improve performance even w/ small nets?} \gl{The deep compression in table III shows it very well}, at least for larger batches when hardware can be fully utilized.

@@

\ra{checkpoint}

@@

To illustrate this point on a larger dataset, we show two examples of
architectures learned by \textit{ShrinkNets} in
Figure~\ref{fig:network_size_evolution}.  The top plot shows the model with the
best test accuracy, with \srm{identical performance to the best static
network?}; the bottom shows a network that slightly under-performs the best in
terms of accuracy but is significantly smaller that the best equivalent
\textit{Static Network} \srm{how much smaller?}.  In the plot, the dashed line
shows the number of neurons in each layer of the original VGG net, and the
shaded regions show the size of the ShrinkNet as it converges (with the darkest
region representing the fully converged network).  Observe that the final
network that is trained looks quite different in the two cases, with the optimal
performing network appearing similar to the original VGG net, whereas the
shrunken network allocates many fewer neurons to the middle layers, and then
additional neurons to the final fewer layers.

>>>>

@@

The results are shown in the top figure of \cref{figure_CIFAR10}, with blue dots
indicating models produced by \shrink and orange dots indicating static networks. 
For each
model, we plot its accuracy and model size. The lines show the Pareto frontier
of models in each of the two optimization settings. ShrinkNets explore the
trade-off between model size and accuracy more effectively. 
%\srm{Summarize
%more quantitatively -- best model performance, model performance drop off for a
%factor of 10 reduction in seize, etc. so that we can repeat a quantitative claim
%in the intro, i.e., ``Note that the best performing ShrinkNets models has 9x.x\%
%accuracy while the best static model has 9x.x\% accuracy, while the ShrinkNets
%model is x times smaller.  In addition, if we give up just 1\% error, ShrinkNets
%finds a model that is z times smaller.'' (If we do this, would be good to
%highlight these points in the figure somehow)}

Note that the best performing ShrinkNets models has $92.07\%$ accuracy which
is identical to the accuracy of the static network, while the ShrinkNets model
is $2.22$ times smaller. In addition, if we give up just 1\% error, ShrinkNets
finds a model that is 35.5 times smaller than any static network that performs
as good or better.

@@

Note that the best performing ShrinkNets models has $96.91\%$ accuracy while the
best static model is only $96.66\%$ accurate, while the ShrinkNets model is $2.51$
times smaller. In addition, if we give up just 0.5\% error, ShrinkNets finds a
model that is 38.6 times smaller than any static network with equivalent accuracy.

@@

A key takeaway of these speedup results is that, unlike local sparsity compression methods, our methods' improvement on size translates directly to higher throughput at inference time~\cite{Han2015}.

@@

@@

To illustrate this point on a larger dataset, we show two examples of
architectures learned by \textit{ShrinkNets} in
Figure~\ref{fig:network_size_evolution}.  The top plot shows the model with the
best test accuracy, with identical performance to the best static
network; the bottom shows a network that slightly under-performs the best in
terms of accuracy but is significantly smaller that the best equivalent
\textit{Static Network}.  In the plot, the dashed line
shows the number of neurons in each layer of the original VGG net, and the
shaded regions show the size of the ShrinkNet as it converges (with the darkest
region representing the fully converged network).  Observe that the final
network that is trained looks quite different in the two cases, with the optimal
performing network appearing similar to the original VGG net, whereas the
shrunken network allocates many fewer neurons to the middle layers, and then
additional neurons to the final fewer layers.
